
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
  %a4paper, % Uncomment for A4 paper size (default is US letter)
  11pt, % Default font size, can use 10pt, 11pt or 12pt
]{public/resume/resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{hyperref}

%------------------------------------------------

\name{Abhay Shukla} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines you use in the \address commands will be converted to symbols, so each address will appear as a single line.
\address{abhayshuklavtr@gmail.com $\vert$ \underline{\href{https://www.linkedin.com/in/shuklabhay/}{https://www.linkedin.com/in/shuklabhay/}} $\vert$ \underline{\href{https://github.com/shuklabhay}{https://github.com/shuklabhay}} $\vert$ \underline{\href{https://shuklabhay.github.io}{https://shuklabhay.github.io}}}% Contact information

%----------------------------------------------------------------------------------------

\begin{document}
\sloppy

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}


  \begin{rSubsection}{FRC 604: Quixilver Robotics}{June 2022 - Present}{Controls (Software) Lead (10-11)}{California}
    
    \item Develop team's competition data collection application, contribute to team's Particle Filter, Holonomic Time Optimized Autonomous Path Planner, and Yearly Robot Control Software.
    
    \item Enhance robot capabilities and localization by utilizing computer vision and environmental sensors.
    
    \item Contribute to a universally used FRC tool TheBlueAlliance: a global competition data aggregation and insight platform.
    
    \item Lead subteams in design, manufacturing, and programming of team robot while training new members to contribute to robot development. Personally attended 20+ STEM community outreach events.
    
    \item 2024 Season: 4th ranked ranked team in California, 12th out of ~3500 participating teams. Won International World Championship Division and two California Regional Events.
    
  \end{rSubsection}
        
  \begin{rSubsection}{UCLA COSMOS (2024 Cluster 1)}{July 2022 - August 2024}{AI Cohort Student}{California}
    
    \item Participated in highly selective 4 week UCLA Neurology and AI Summer Program (<4.6\% acceptance rate).
    
    \item Rapidly developed comprehensive understanding of transformers, recurrent networks, advanced regression, reinforcement learning, convolutional models, and training optimization.
    
    \item Started program without any prior knowledge, created and optimized numerous architectures for given use cases.
    
  \end{rSubsection}
        
  \begin{rSubsection}{Bay Area STEM Academy}{April 2023 - Present}{Cofounder}{California}
    
    \item Cofounded non-profit organization to host accessible and engaging free STEM camps for local elementary, middle, and high school students.
    
    \item Developed engaging curriculums, managed logistical aspects, recruited mentors, and effectively taught multiple in-person and online camps encompassing diverse STEM fields.
    
    \item Impacted 500+ students and raised \$4800+ to support organization costs, local robotics team STEM outreach initiatives, and underserved Indian children healthcare foundation.
    
  \end{rSubsection}
        
  \begin{rSubsection}{Leland Speech and Debate (NSDA)}{August 2022 - Present}{Varsity Speaker}{California}
    
    \item Develop robust arguments and refine argumentation skills on national and international issues through competitive debate.
    
    \item Rapidly synthesize compelling and appealing speeches using current events and existing knowledge.
    
    \item Competed in 20+ tournaments as a member of the selective, nationally ranked (3rd out of 3550+ NSDA programs) team.
    
  \end{rSubsection}
        
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

  
  \begin{rSubsection}{StereoSampleGAN}{}{GitHub Repo: \underline{\href{https://github.com/shuklabhay/stereo-sample-gan}{https://github.com/shuklabhay/stereo-sample-gan}}}{}
       
    \item Introduces a novel machine learning architecture to generate stereo, time-frequency representations of audio samples.
        
    \item Independent research project, pending publishing. Continuation of UCLA COSMOS 2024 Research.
        
    \item Takeaways: Advanced ML Training Techniques, Attention/Transformers, GANs, Signal Processing, Data Representation, Data Collection, AI Research.
        
  \end{rSubsection}
      
  \begin{rSubsection}{Quickscout}{}{GitHub Organization (Private Team Project): \underline{\href{https://github.com/frc604}{https://github.com/frc604}}}{}
       
    \item Provides intuitive and easily modifiable data collection interfaces for effective data collection and flexible control over data capture/visualization.
        
    \item Integrates collected data and external sources to create insightful visualizations, enabling comprehensive competitive analysis.
        
    \item Comprehensive data collection enables the creation of new metric visualizations on demand and ultra-informed strategic decisions.
        
    \item Mainly led app development, trained 10+ team members in web dev to build app in a modular to build and adapt the app to yearly games.
        
    \item Actively used by FRC604: 100+ users, data collected for 670+ robots.
        
    \item Takeaways: Dynamic App Design, Insightful Data Visualization, Big Data Collection and Processing, Full Stack Development, Intuitive Interface Design
        
  \end{rSubsection}
      
  \begin{rSubsection}{Domotron (FRC604 2024 Robot)}{}{Robot Website: \underline{\href{https://604robotics.com/2023-2024-crescendo/}{https://604robotics.com/2023-2024-crescendo/}}}{}
       
    \item Maximized ranking points by incorporating speaker, amplifier, and trap scoring capabilities.
        
    \item Developed physics-based shot calculations, driver control automation, competitive autonomous routines.
        
    \item Designed climber winch mechanism and vertical elevator.
        
  \end{rSubsection}
      
  \begin{rSubsection}{VelocityDraft}{}{Website: \underline{\href{https://shuklabhay.github.io/velocity-draft/}{https://shuklabhay.github.io/velocity-draft/}}}{}
       
    \item Leverages user writing abilities and essay deadlines to algorithmically determine best order of essay writing to maximize writing and review time and prevent overwhelming users.
        
    \item Recieved third place prize in OneHacks III Hackathon.
        
    \item Takeaways: GitHub Action Automation, Algorithmic Problem Solving, Website Interface Design
        
  \end{rSubsection}
      
	
\end{rSection}
    
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	\textbf{Leland High School} \hfill \textit{Expected June 2026} \\
	HS Junior \hfill \textit{San Jose, CA}
	
\end{rSection}

%----------------------------------------------------------------------------------------
    %	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

  \begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Relevant Fields & AI/ML, Robotics, Signal Processing, CAD, 3D Printing, Webdev/Appdev, Digital Audio Production, Graphic Design, Video Editing \\
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
    % HONORS & AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards}

  \begin{itemize}
      \setlength\itemsep{-0.7em} % Adjust the space between items
        
      \item NextFlex FlexFactor: Santa Clara Regional Winner \hfill May 2024
              
      \item NSE Level 2: Silver Distinction \hfill May 2024
              
      \item OneHacks III Hackathon: 3rd Place Submission \hfill August 2023
              
      \item PSVA: Gold Award \hfill July 2023
              
      \item CFL Speech 2: Finalist \hfill December 2022
              
      \item SCU/SVUDL Invitational: PF Finalist \hfill November 2022
              


    \end{itemize}

\end{rSection}

\end{document}
