
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
  %a4paper, % Uncomment for A4 paper size (default is US letter)
  10pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume}

\usepackage{times}
\usepackage{hyperref}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\frenchspacing

%------------------------------------------------

\name{Abhay Shukla} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines you use in the \address commands will be converted to symbols, so each address will appear as a single line.
\address{abhayshuklavtr@gmail.com $\vert$ \underline{\href{https://www.linkedin.com/in/shuklabhay/}{https://www.linkedin.com/in/shuklabhay/}} $\vert$ \underline{\href{https://github.com/shuklabhay}{https://github.com/shuklabhay}} $\vert$ \underline{\href{https://shuklabhay.github.io}{https://shuklabhay.github.io}}}% Contact information

%----------------------------------------------------------------------------------------

\begin{document}
\sloppy

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}


  \begin{rSubsection}{Stanford Center for Biomedical Informatics Research}{November 2024 - Present}{Gevaert Lab Student Researcher}{California}
    
    \item Developed physics-based neural networks for anatomically accurate image augmentations (tissue compression, stages in respiratory/cardiac phases, etc), significantly improving cancer model accuracy.
    
    \item Implemented computer vision models (CNNs, Vision Transformers) for precise breast region segmentation.
    
    \item Designed Python data processing pipelines for efficient handling of large-scale biomedical datasets on multi-node systems.
    
  \end{rSubsection}
        
  \begin{rSubsection}{FRC Team 604: Quixilver Robotics}{June 2022 - Present}{Controls/Software Lead (10)}{California}
    
    \item Implemented real-time computer vision systems for autonomous robot navigation and object detection.
    
    \item Designed stratgic robotic mechanisms and integrated multi-modal sensors for optimal robot performance and reliability.
    
    \item Developed competition data collection infrastructure and visualization tools analyzing 1000+ competition matches with 200+ users.
    
    \item Achieved top 0.1\% international ranking (12/10,000+ teams) through integrated hardware-software optimization.
    
  \end{rSubsection}
        
  \begin{rSubsection}{UCLA COSMOS (Brain-Inspired Computing/Artificial Intelligence Cohort)}{July 2024 - August 2024}{Student Researcher}{California}
    
    \item Developed neural networks to model rat hippocampus activity, perform image geolocation, and recognized handwritten characters.
    
    \item Applied neurobiological priors to computational modeling techniques using Jax, Torch, and TensorFlow.
    
  \end{rSubsection}
        
  \begin{rSubsection}{Pavyl}{January 2025 - Present}{Software Design Advisor}{California}
    
    \item Evaluated memory and computational efficiency of infinite context large language models.
    
    \item Recommended app optimizations for model accuracy, external tool integration, and response time.
    
  \end{rSubsection}
        
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

  
    \begin{rSubsection}{StereoSampleGAN - \textit{\underline{\href{https://github.com/shuklabhay/stereo-sample-gan}{Independent Research Project}}}}{}{}{}
        
      \item Developed pioneering generative adversarial network addressing critical research gaps in high-quality stereo audio synthesis.
          
      \item Implemented efficient image-like audio representations and efficient model training techniques.
          
      \item Achieved 85\% quality improvement and 25x training time reduction compared to industry benchmarks
          
      \item Skills: Time-Series Data, Multimodality, PyTorch, NumPy, DSP
          
    \end{rSubsection}
        
    \begin{rSubsection}{Vox Transformis - \textit{\underline{\href{https://shuklabhay.github.io/static/projects/vox-transformis/vt_poster.png}{Science Fair Research Project}}}}{}{}{}
        
      \item Developed LLM-based multimodal musical translation system preserving rhythmic, melodic, and artistic features of sung audio.
          
      \item Won Honorable Mention Award out of 977 participants at 2025 Santa Clara Synopsys Science Fair.
          
      \item Project presented to San Jose Mayor Matt Mahan and recognizd by the City of San Jose for impact on local language preservation.
          
      \item Skills: Model Ensembling, LLM Manipulation, Signal Processing, Model Context Protocol
          
    \end{rSubsection}
        
    \begin{rSubsection}{SporeStrike - \textit{\underline{\href{https://shuklabhay.github.io/static/projects/sporestrike/FlexFactor_SporeStrike_pitch.pdf}{Entrepreneurship Project}}}}{}{}{}
        
      \item Designed computational models for drone-based fungal infection treatment system, created prototype 3D printed components.
          
      \item Presented project to civil and aerospace engineering pannel; won first place/260 competitors at 2024 FlexFactor Entrepreneurship Championships.
          
      \item Skills: Real-World System Design, CAD, 3D Printing
          
    \end{rSubsection}
        

\end{rSection}
    
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
  
  \textbf{Leland High School} \hfill \textit{4.00 UW A-G} \\
  Junior (Expected Graduation 2026) \hfill \textit{San Jose, CA}
	
\end{rSection}

%----------------------------------------------------------------------------------------
    %	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
 
  \begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Technical Fields & AI/ML, Data Visualization and Analysis, Robotics, Signal Processing, 3D Printing, Web Development \\
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
    % HONORS & AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards}

  \begin{itemize}
      \setlength\itemsep{-0.7em} % Adjust the space between items
        
      \item City of San Jose Recognition for AI-driven Efforts for Local Language Preservation \hfill 2025
              
      \item WCP CADathon/Robot Design Challenge Finalist (Top 1\%, 1000+ participants) \hfill 2024
              
      \item FRC604: World Championship Milstein Division Winner (12/3500 Internationally, 4/300 in CA) \hfill 2024
              
      \item OneHacks III Hackathon: Third Place (3/120 Internationally) \hfill 2023
              


    \end{itemize}

\end{rSection}

\end{document}
